BLAST: Block Applications for Things

### 2022-03-04 demo-eswc22/paper.tex
change screenshot, add description

\begin{figure}
\includegraphics[width=\textwidth]{Blast Screenshot.png}%im Ordner sind noch 2 alternative Screenshots
\caption{Graphical user interface of the BLAST programming environment.} \label{fig1}
\end{figure}

When choosing the vocabulary for our block-based language BLAST, we resorted to a mixture of natural language and computer language \cite{8120404}.
This means that in BLAST, the blocks are arranged into readable sentences, as in a natural language, but the blocks also contain a few technical programming terms, such as ''repeat while true'' instead of ''forever''.
This makes the BLAST vocabulary both understandable for beginners, but still flexible.

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{screenshot.png}%im Ordner sind noch 2 alternative Screenshots
\caption{Example BLAST program} \label{fig1}
\end{figure}

When choosing the vocabulary for our block-based language BLAST, we resorted to a mixture of natural language and computer language \cite{8120404}.
This means that in BLAST, the blocks are arranged into readable sentences, as in a natural language, but the blocks also contain a few technical programming terms, such as ''repeat while true'' instead of ''forever''.
This makes the BLAST vocabulary both understandable for beginners, but still flexible. Take the program in Figure \ref{fig1} as an example. One should easily figure out that it is used to toggle a Bluetooth LED light. Every time the user pushes the top-left button on their StreamDeck down, the LED light is toggled between red and off.
